Distanced-based VOCC analysis

### 2019-06-08 analysis/VOCC/dist-vocc.Rmd
calculate age at maturity with random effect of year

```{r}
out <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2005,
  skip_time = 2011,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
# glimpse(out)
```

```{r}
gvocc <- plot_vocc(out,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 100,
  fill_col = "var_1_e",
  fill_label = "Mean\ntemperature\n2013-2017",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D"
)
gvocc <- gvocc + ggtitle("VOCC vectors for <0.5°C change")
gvocc
```

```{r}
gtrend <- plot_vocc(out,
  fill_col = "units_per_decade",
  fill_label = "°C per decade",
  raster_alpha = 1,
  vec_aes = NULL
)
gtrend <- gtrend + ggtitle("Bottom temperature trend 2005-2017")
gtrend
```

@@

```{r}
biomass <- readRDS("data/maturity-biomass-data-pop-1n3.rds")
#doy <- data %>% select(fishing_event_id, DOY)
#biomass <- left_join(biomass, doy)
```

@@

nd <- nd %>% mutate(year = as.integer(year)) %>% 
  # filter(ssid!=3) %>% 
  filter(ssid!=4) %>% 
  filter(ssid!=16) %>%
  dplyr::filter(year > 2003)

@@

```{r}
predictions <- adult_predictions
predictions$est_exp <- exp(predictions$est)
# sqrt_trans <- scales::trans_new(
#   name = "logp",
#   trans = function(x) sqrt(x),
#   inverse = function(x) ((x))^2,
#   breaks = scales::log_breaks()
# )
p_adult <- plot_map(predictions, "est_exp") + 
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Pacific Ocean Perch mature biomass") + theme(legend.position = c(0.9, 0), legend.justification = c(0.9, 0), legend.title = element_blank() ) 
print(p_adult)
```

```{r}
adult_predictions$est_exp <- exp(adult_predictions$est)
adult <- make_vector_data(adult_predictions,
  ssid = c(1,3),
  start_time = 2005,
  skip_time = 2011,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) # vector of plus/minus threshold(s) to define match.
)
#glimpse(adult )
```

```{r eval=FALSE}
gvobiomass <- plot_vocc(adult,
  # low_col = "yellow",
  # mid_col = "grey",
  # high_col = "black",
  # vec_aes = "units_per_decade",
  # vec_lwd_range = c(0.7,0.005 ),
  # vec_alpha = 0.7,
  # max_vec_plotted = 30,
  fill_col = "var_1_e",
  fill_label = "Mean mature \nbiomass (kg/m2)\n in 2013-2017",
  raster_alpha = 1,
  viridis_option = "C",
  vec_aes = NULL
)
gvobiomass <- gvobiomass +
  ggtitle("Pacific Ocean Perch")

@@

```{r}
biotrend_ad <- plot_vocc(adult,
  fill_col = "units_per_decade",
  fill_label = "Mature \nbiomass trend \n(kg/m2/decade)\nfor 2005-2017",
  raster_alpha = 1,
  vec_aes = NULL
)
biotrend_ad
```

```{r}
predictions <- imm_predictions
predictions$est_exp <- exp(predictions$est)

p <- plot_map(predictions, "est_exp") + 
  scale_fill_viridis_c(trans = "sqrt", option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
print(p)
```

```{r}
imm_predictions$est_exp <- exp(imm_predictions$est)

@@

```{r}
biotrend_im <- plot_vocc(out_im,
  fill_col = "units_per_decade",
  fill_label = "Immature \nbiomass trend \n(kg/m2/decade)\nfor 2005-2017",
  raster_alpha = 1,
  vec_aes = NULL
)
biotrend_im
```

```{r}
png(file = "exploratory-pop-figs.png",   # The directory you want to save the file in
res = 600,
units = 'in',
width = 14, # The width of the plot in inches
height = 12) # The height of the plot in inches

>>>>

```{r}
out <- make_vector_data(temperature,
  ssid = c(1,3),
  start_time = 2005,
  #skip_time = 2011,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2, 2),
  thresholds = c(0.5) # vector of plus/minus threshold(s) to define climate match.
)
# glimpse(out)
```

```{r}
gvocc <- plot_vocc(out,
  low_col = "white",
  mid_col = "white",
  high_col = "grey87",
  vec_aes = "distance",
  vec_lwd_range = c(0.2, 0.5),
  max_vec_plotted = 100,
  fill_col = "var_1_e",
  fill_label = "Mean\ntemperature\n2013-2017",
  raster_alpha = 1,
  vec_alpha = 0.25,
  axis_lables = FALSE,
  viridis_option = "D",
  transform_col = no_trans
)
gvocc <- gvocc + ggtitle("VOCC vectors for <0.5°C change")
gvocc
```

```{r}
gtrend <- plot_vocc(out,
  fill_col = "units_per_decade",
  fill_label = "°C per decade",
  raster_alpha = 1,
  vec_aes = NULL,
  transform_col = no_trans
)
gtrend <- gtrend + ggtitle("Bottom temperature trend 2005-2017")
gtrend
```

@@

```{r}
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)

events <- readRDS("analysis/VOCC/data/event-data-pop-1n3.rds")
fish <- readRDS("analysis/VOCC/data/bio-data-pop-1n3.rds")

biomass <- split_catch_maturity (events, fish, 
  survey = c("SYN HS","SYN QCS"), 
  years = NULL,
  cutoff_quantile = c(.9995),
  plot = TRUE
)

saveRDS(biomass, file = "analysis/VOCC/data/maturity-biomass-data-pop-1n3-re.rds")

# disagreement between catch_weight and bio sample for single fishing event with 17 large POP. 
# events[events$fishing_event_id==1506954,]$catch_weight
# fish[fish$fishing_event_id==1506954,]$length
# tidy_sets[tidy_sets$fishing_event_id==1506954,]$catch_weight

```

```{r}
biomass <- readRDS("data/maturity-biomass-data-pop-1n3-re.rds")
#doy <- data %>% select(fishing_event_id, DOY)
#biomass <- left_join(biomass, doy)
```

@@

nd <- nd %>% mutate(year = as.integer(year)) %>%
  # dplyr::filter(year > 2003) %>% 
  filter(ssid!=3) %>% 
  filter(ssid!=4) %>% 
  filter(ssid!=16) 
#unique(biomass$year)

@@

```{r}
predictions <- adult_predictions
predictions$est_exp <- exp(predictions$est)*10000

breaks <- scales::trans_breaks(fourth_root_power[["transform"]], fourth_root_power[["inverse"]], n=5) 
labels <- function(x) { format(x, digits=1) }

p_adult <- plot_map(predictions, "est_exp") + 
  scale_fill_viridis_c(trans = fourth_root_power, breaks=breaks, labels = labels, option = "C") +
  ggtitle("Pacific Ocean Perch mature biomass") + theme(legend.position = c(0.9, 0), legend.justification = c(0.9, 0), legend.title = element_blank() ) 
print(p_adult)
```

```{r}
adult_predictions$est_exp <- exp(adult_predictions$est)*10000
adult <- make_vector_data(adult_predictions,
  ssid = c(1,3),
  start_time = 2005,
  #skip_time = 2011,
  input_cell_size = 2,
  scale_fac = 1,
  delta_t_total = 10,
  delta_t_step = 2,
  indices = c(1, 1, 1, 2, 2, 2, 2),
  variable_names = "est_exp",
  thresholds = c(0.001) # vector of plus/minus threshold(s) to define match.
)
#glimpse(adult )
```

```{r eval=FALSE}
gvobiomass <- plot_vocc(adult,
  # low_col = "yellow",
  # mid_col = "grey",
  # high_col = "black",
  # vec_aes = "units_per_decade",
  # vec_lwd_range = c(0.7,0.005 ),
  # vec_alpha = 0.7,
  # max_vec_plotted = 30,
  fill_col = "var_1_e",
  fill_label = "Mean mature \nbiomass (kg/ha)\n in 2011-2017",
  raster_alpha = 1,
  viridis_option = "C",
  vec_aes = NULL,
  transform_col = fourth_root_power
)
gvobiomass <- gvobiomass +
  ggtitle("Pacific Ocean Perch")

@@

```{r}
biotrend_ad <- plot_vocc(adult,
  fill_col = "units_per_decade",
  fill_label = "Mature \nbiomass trend \n(kg/ha/decade)\nfor 2005-2017",
  raster_alpha = 1,
  vec_aes = NULL,
  transform_col = fourth_root_power
)
biotrend_ad
```

```{r}
predictions <- imm_predictions
predictions$est_exp <- exp(predictions$est)*10000

p <- plot_map(predictions, "est_exp") + 
  scale_fill_viridis_c(trans = fourth_root_power, breaks=breaks, labels = labels, option = "C") +
  ggtitle("Prediction (fixed effects + all random effects)")
print(p)
```

```{r}
imm_predictions$est_exp <- exp(imm_predictions$est)*10000

@@

```{r}
biotrend_im <- plot_vocc(out_im,
  fill_col = "units_per_decade",
  fill_label = "Immature \nbiomass trend \n(kg/ha/decade)\nfor 2005-2017",
  raster_alpha = 1,
  vec_aes = NULL,
  transform_col = fourth_root_power
)
biotrend_im
```
```{r}
png(file = "POP-maturity-year-re.png",   # The directory you want to save the file in
res = 600,
units = 'in',
width = 8, # The width of the plot in inches
height = 10)

plot_mat_ogive(m)
dev.off()
```

```{r}
png(file = "exploratory-pop-figs-trans.png",   # The directory you want to save the file in
res = 600,
units = 'in',
width = 14, # The width of the plot in inches
height = 12) # The height of the plot in inches
